Learning Heuristics of SAT by Graph Neural Networks

### 2018-12-15 report/paper.tex
misc

We use PyTorch framework to implement the neural networks and reinforcement learning.
The code we use to implement message-passing neural network and gated-graph neural network 
are based on open-sourced repositories on Github 
\footnote{https://github.com/JamesChuanggg/ggnn.pytorch} 
\footnote{https://github.com/priba/nmp\_qc}.
The policy network is a shallow neural network with three hidden layers.

>>>>

We use PyTorch framework to implement the neural networks and reinforcement learning.
The code we use to implement message-passing neural network and gated-graph neural network 
are adapted from open-sourced repositories on Github 
\footnote{https://github.com/JamesChuanggg/ggnn.pytorch} 
\footnote{https://github.com/yujiali/ggnn}.
The policy network is a shallow neural network with three hidden layers.
